---
title: "Habits"
author: John Doe
date: March 22, 2005
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"roller"` is an [R](http://www.r-project.org/) package 
that allows us to simulate rolling a die/device.

* `device()` creates a dice object (of class `"device"`)
* `roll()` rolls a device object, yielding a `rolls` object.
* `plot()` method for a `"rolls"` object to plot frequencies of each side rolled.
* `summary()` method for a `"rolls"` object gives a frequency table of the sides rolled.
* `"["` extract method for a `"rolls"` object extracts the element at the nth roll.
* `"[<-"` method allows us to change certain rolls outcomes.
* `"+"` method adds rolls to an already-rolled rolls object.


## Motivation

This package has been created to satisfy a homework problem, and also to learn the tools necessary to create a fully functional R package.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```{r}
# development version from GitHub:
#install.packages("devtools") 
# install "roller" (without vignettes)
#devtools::install_github("stat133-f18/hw-stat133-colefh/workout3/roller")
# install "roller" (with vignettes)
#devtools::install_github("colefh/Workout3/roller", build_vignettes = TRUE)
```


## Usage

```{r}
library(roller)
# default die
device1 <- device()
device1

# 1 roll of device1
roll(device1, times = 1)

# 10 rolls of device1
roll10 <- roll(device1, times = 10)
roll10

# summary
summary(roll10)

# 100 rolls
roll100 <- roll(device1, times = 100)

# summary
summary(roll100)

# plot
plot(roll100)

# extract
roll100[100]

# change
roll100[100] <- 1
roll100[100]
roll100[100] <- 2
roll100[100]

# add
roll200 <- roll100 + 100
roll200

# summary
summary(roll200)
```
